NIRCam Faint and Bright Flux Calibration Plan

### 2017-04-09 ms.tex
I began describing the UKIRT photometric data.
I added a figure to show the expected fluxes of the new program compared to the existing stars in the database.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.6\columnwidth]{nircam_wide_filters.png}
\caption{The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}. The three values are shown as upper, middle and lower limit error bars respectively. For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red). Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.}\label{fig:JWStcalsWideF}
\end{figure}

@@

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.6\columnwidth]{nircam_wide_filters.png}
\includegraphics[width=.3\columnwidth]{calspec_and_new_clust.pdf}
\caption{{\it Left:} The NIRCam subarray saturation, full frame saturation and 10~$\sigma$ sensitivity limits for wide band imaging from \citet{gordon2011fluxplan2}. The three values are shown as upper, middle and lower limit error bars respectively. For comparison, three classes of JWST calibrators are shown: hot stars including white dwarfs (blue), A-type stars (green) and G-type stars (red).
Additional faint calibrators are needed to extend the sample from \citet{gordon2011fluxplan2} towards the faint limits of NIRCam.
{\it Right:} The new expected G2 V calibrators as compared to the faintest G-type star in the calibration plan.}\label{fig:JWStcalsWideF}
\end{figure}

@@

We observed all three clusters with WFCAM on the UKIRT telescope.
This is the same instrument, pipeline and telescope for the UKIDSS survey.
As recommended by the pipeline team, we used aperture photometry number 3 (1\arcsec\ radius) for the fluxes in the J, H and K bands.
